First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q^{2}

### 2020-01-03 MY_PUBLICATIONS/PRL/draft_v3/body.tex
updated draft 3

\indent Both experimental and theoretical reduced cross sections were extracted from the measured (or model) cross sections for each data set independently and were
averaged for overlapping bins in $p_{r}$. 

@@

\noindent The reduced cross sections are defined as follows:

@@

\indent At recoil angles $\theta_{nq}=75^{o}$ [Fig. \hyperref[fig:fig1]{1(c)}], all models agree and are sensitive to momentum distributions up to $p_{r}\sim$300 MeV/c. Beyond $p_{r}\sim$300 MeV/c, FSIs become
dominant and exhibit a similar behaviour among all models which obscures any possibility of extracting the momentum distributions at these angles. At smaller recoil angles, $\theta_{nq}=35^{o}$ and $45^{o}$ 
[Figs. \hyperref[fig:fig1]{1(a), 1(b)}], the Paris and AV18 calculations show sensitivity to momentum distributions and are within good agreement whereas the CD-Bonn calculation exhibits
a different behaviour beyond $p_{r}\sim$300 MeV/c which indicates a larger sensitivity to the different NN-potentials at higher missing momenta.

%The data is compared to the results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$.  The overlay of the Hall A data (cyan) in Fig. \ref{fig:fig1}
%provides a continutity to the data from this experiment in the transition from low (80 MeV/c) to high (580, 750) MeV/c missing momentum settings in which there
%was no data. There is also an overall good agreement between the two experiments in the regions in which they overlap in $p_{r}$. \\
%\indent At larger neutron recoil angles of $\theta_{nq}\sim75^{o}$ [Fig. \hyperref[fig:fig1]{1(c)}], the data follows the CD-Bonn PWIA (momentum distributions) up to $p_{r}\sim $100 MeV/c, and at $p_{r}\gtrsim$300 MeV/c, the FSIs become the dominat process and exhibit a
%smaller falloff with $p_{r}$ which obscures any possibility of extracting the momentum distributions. This behaviour of FSI with larger recoil angles was predicted by the GEA\cite{Sargsian_2001,PhysRevC.56.1124} and was verified in previous experiments\cite{PhysRevLett.107.262501,PhysRevLett.98.262502}.
%This experiment kinematics moves away from larger recoil angles and focuses on fowards angles at $\theta_{nq}\sim 40^{o}$ where the momentum distributions become accessible. As a result, our data at larger recoil angles
%is statistically limited. \\
%\indent For recoil angles at $\theta_{nq}=35^{o}$ and $45^{o}$ shown in Figs. \hyperref[fig:fig1]{1(a)} and \hyperref[fig:fig1]{1(b)},  all models predict similar behaviour of the
%momentum distribution for recoil momenta up to $p_{r}\sim$300 MeV/c which the data verifies. At larger $p_{r}$, however, the momentum distributions become increasingly sensitive to the different
%NN potentials, mainly a difference between the CD-Bonn and either the Paris or AV18 is observed. \\
%\indent In Fig. \hyperref[fig:fig1]{1(a)} for example, the data is clearly sensitive to the CD-Bonn momentum distributions between recoil momenta of $300\lesssim p_{r}\lesssim750$ MeV/c before transitioning
%to the Paris/AV18 potentials which is a behaviour that is not well described by any of the models. For recoil angles in Fig. \hyperref[fig:fig1]{1(b)},
%a similar behaviour can be observed, as the data is sensitive to the CD-Bonn momentum distributions but only up to $p_{r}\sim 580$ MeV/c as FSIs start to dominate at lower $p_{r}$ as opposed to Fig. \hyperref[fig:fig1]{1(a)}.
%For $p_{r}>580$ MeV/c, the data again exhibits a behaviour at the high momentum tails which either the CD-Bonn, Paris or AV18 potentials are unable to describe.\\

>>>>

\indent Both experimental and theoretical reduced cross sections were extracted from the measured (or model) cross 

@@

\noindent sections for each data set independently and were averaged for overlapping bins in $p_{r}$. The reduced cross sections are defined as follows:

@@

\indent For the recoil angles shown in Fig. \hyperref[fig:fig1]{1(a)-(c)}, all models agree and the cross sections are dominated by the PWIA up to $p_{r}\sim$300 MeV/c, which corresponds to the long-range part
of the NN-potential which is well understood. Beyond $p_{r}\sim$300 MeV/c, at recoil angles $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig1]{1(a), 1(b)}], the Paris and AV18 model cross sections are dominated by
the PWIA and are within good agreement whereas the CD-Bonn calculation exhibits a different behaviour which indicates a larger sensitivity to the different NN-potentials
at higher missing momenta. At recoil angles $\theta_{nq}=75^{o}$ [Fig. \hyperref[fig:fig1]{1(c)}] and $p_{r}>300$MeV/c, FSIs become dominant and exhibit a similar behaviour among all models which obscures any possibility
of extracting the momentum distributions at these angles. \\

### 2020-01-03 MY_PUBLICATIONS/PRL/draft_v3/introduction.tex
updated draft 3

\indent Previous deuteron electro-disintegration experiments performed at Jefferson Lab (JLab) have helped confirmed various of the abovementioned theoretical predictions as well as constrain and quantify the contributions from FSIs, MECs and ICs on
the $^{2}H(e,e'p)n$ cross-section to determine the kinematics at which they are either suppressed (MECs and ICs) or under control (FSIs). The first of these was performed in Hall A \cite{PhysRevLett.89.062301}
at a relatively low momentum transfer of $Q^{2}=0.665$ (GeV/c)$^{2}$ and neutron recoil momenta up to $p_{r} = $ 550 MeV/c where it was shown that for $p_{r}>$ 300 MeV/c, FSIs, MECs and ICs dominate the cross section and
had to be included in Arenh\"{o}vel's calculations \cite{PhysRevC.43.1022, PhysRevC.46.455, PhysRevC.52.1232, PhysRevC.55.2214} for a satisfactory agreement between theory and data. \\
\indent The next experiment was performed in Hall B \cite{PhysRevLett.98.262502} using the CEBAF Large Acceptance Spectrometer (CLAS) which measured a wide variety of kinematic settings
giving an overview of the $^{2}H(e,e'p)n$ reaction kinematics. This was the first experiment to probe
the deuteron at high momentum transfers ( 1.75 $\leq Q^{2}\leq$ 5.5 (GeV/c)$^{2}$) and presented angular distributions of cross-sections that exhibited a strong angular dependence of FSI with neutron recoil angles peaking
at $\theta_{nq} \sim 70^{o}$ which confirmed the onset of the GEA\cite{Sargsian_2001,PhysRevC.56.1124}.
The cross sections versus neutron recoil momenta up to $p_{r}\sim$2 GeV/c were also presented, however, statistical limitations made it necessary to integrate over a wide angular range making it impossible to control
contributions from FSIs, MECs and ICs. \\
\indent Finally, a third $^{2}H(e,e'p)n$ experiment was performed in Hall A \cite{PhysRevLett.107.262501} at $Q^{2} = 3.5\pm0.25$ (GeV/c)$^{2}$ and recoil momenta up to 550 MeV/c. The angular distributions of
the cross-section ratio ($R = \sigma_{exp}/\sigma_{PWIA}$) presented saw agreement in shape with the angular distributions in Hall B\cite{PhysRevLett.98.262502} with FSI peaking at $\theta_{nq}\sim70^{o}$. With the increased statistics in Hall A, a direct comparison of the momentum distributions between data and theory could be made for specific $\theta_{nq}$ bins. For the first time, at $\theta_{nq}=35\pm5^{o}$ and $45\pm5^{o}$, theoretical models showed a sensitivity to the NN-potential used in the deuteron wavefunction that was not obscured by FSI contributions to the cross section data.\\

>>>>

%---------D(e,e'p) Experiments at Q2 < 1-------- 
\indent Previous deuteron electro-disintegration experiments performed at lower $Q^{2}$ ($Q^{2}<1$ (GeV/c)$^{2}$)\cite{sargsian_2015} have helped quantify the contributions from FSIs, MECs and ICs on
the $^{2}H(e,e'p)n$ cross-section to determine the kinematics at which they are either suppressed (MECs and ICs) or under control (FSIs).  At $p_{r}<300$ MeV/c, theoretical
calculations by Arenhovel\cite{Arenhovel_1976} showed that FSIs, MECs and ICs contributions mutually cancel leaving the PWIA as the dominant contribution to the cross section which
the data confirmed. Beyond $p_{r}\sim300$ MeV/c, however, the data showed that these processes do not mutually cancel and had to be included in the theory for a satisfactory agreement. \\
\indent The first $^{2}H(e,e'p)n$ experiments at high $Q^{2}$ were carried out at Jefferson Lab (JLab) in Halls A\cite{PhysRevLett.89.062301} and B\cite{PhysRevLett.98.262502}. Both
experiments concluded that the cross-sections exhibited a strong angular dependence of FSI with neutron recoil angles peaking
at $\theta_{nq} \sim 70^{o}$ which confirmed the onset of the GEA\cite{Sargsian_2001,PhysRevC.56.1124}. In Hall B, the CEBAF Large Acceptance Spectrometer (CLAS) measured a wide variety
of kinematic settings giving an overview of the $^{2}H(e,e'p)n$ reaction kinematics, however, statistical limitations made it necessary to integrate over a wide angular range making
it impossible to control contributions from FSIs, MECs and ICs. \\
\indent In Hall A, the pair of high resolution spectrometers (HRS) made it possible to measure the dependence of the cross section
with recoil momenta up to $p_{r}=550$ MeV/c at a variety of neutron recoil angles ($\theta_{nq}$). For the first time, at $\theta_{nq}=35\pm5^{o}$
and $45\pm5^{o}$, theoretical models showed a sensitivity to the NN-potential used in the deuteron wavefunction that was not obscured by FSI contributions to the cross section data.\\
